### 2016-03-15 paper.tex
Use initials in aknowledgments
Comment out all graphics in manuscript

\begin{figure}[h]
    \includegraphics[width=0.65\textwidth]{figures/turbine.eps}

@@

\begin{figure}
    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}

@@

    \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}

@@

    \includegraphics[clip,trim=0.01in 0 0 0,
    width=\textwidth]{figures/tank_cross_section}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/perf_covers.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/k_contours.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}

@@

This study was supported by the Department of Energy (DOE), Office of Energy
Efficiency and Renewable Energy (EERE), Wind and Water Power Technologies Office
(WWPTO). Authors Bachant and Wosnik acknowledge additional support from the
National Science Foundation, award 1150797. Sandia National Laboratories is a
multi-program laboratory managed and operated by Sandia Corporation, a wholly
owned subsidiary of Lockheed Martin Corporation, for the U.S. Department of
Energy's National Nuclear Security Administration under contract
DE-AC04-94AL85000.

>>>>

\begin{figure}[h]
    % \includegraphics[width=0.65\textwidth]{figures/turbine.eps}

@@

\begin{figure}
    % \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}

@@

    % \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}

@@

    % \includegraphics[clip,trim=0.01in 0 0 0, width=\textwidth]{figures/tank_cross_section}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}

@@

\begin{figure}
    % \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}

@@

\begin{figure}
    % \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/perf_covers.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/no_blades_all.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/meancontquiv.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/k_contours.eps}

@@

\begin{figure}
    % \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}

@@

This study was supported by the Department of Energy (DOE), Office of Energy
Efficiency and Renewable Energy (EERE), Wind and Water Power Technologies Office
(WWPTO). Authors PB and MW acknowledge additional support from the National
Science Foundation, award 1150797. Sandia National Laboratories is a
multi-program laboratory managed and operated by Sandia Corporation, a wholly
owned subsidiary of Lockheed Martin Corporation, for the U.S. Department of
Energy's National Nuclear Security Administration under contract
DE-AC04-94AL85000.
